\section{Game Rules}
\label{sec:rules}

\begin{enumerate}
  \item The game, called \emph{\gamename}, is played in the arena defined in
        Specification~\ref{spec:arena}. The objective is to collect 'apples' from
        a central location and return them to your scoring zone.
  \item There are 3 kinds of Apples, detailed below:
  \begin{enumerate}
      \item - Red Apples are easy to collect and score few points.
      \item - Golden Apples are harder to collect but score more points.
      \item - Rotten Apples carry negative points.            
  \end{enumerate}
  \item There will be 2 robots in each match.
  \item Each robot has a 'market stall' in their scoring zone which allows robots
        to score bonus points by placing their collected apples on it.
  \item The 'market stall' has 2 tiers as shown in ????????. Robots score
        more points for placing apples on the higher tier.
  \item The points awarded for putting each type of apple in each scoring zone is
        as follows:
        ????? table ?????
  \item The Golden Apples start on a 'tree' constructed in the centre of the area
        as detailed on \\ref{}
  \item The Red Apples and Rotten Apples start on the floor around the base of the
        tree as specified in \\ref{}
  \item There are 2 possible starting configurations for the Red Apples and Rotten Apples.
        Before each match, \staff will set up the area in one of the 2 configurations
        chosen randomly with 50/50 probablilty.
  \item Participating teams must present their robots to match officials before
        the start of matches, as regulated by the match officials. Non-compliant
        teams may be disallowed from participating.
  
  \item \org may have any number of match officials within the arena, including
        during the course of matches.
  \item At the start of each match, robots must be entirely within their
        starting zones, as defined in \ref{fig:arena}.
  \item At the start of each match, teams will be permitted to lean into the
        arena and start their robots.
  \item Each match lasts $120$ ??????check???? seconds.
  \item Teams may be disqualified from one or all matches by match officials,
        for non-compliance with regulations, lateness to the match, or any other
        reason at the discretion of the judge. Teams disqualified before the
        start time of a match will not be permitted to enter a robot.
  \item TIES?
\end{enumerate}

\section{Scoring}
\label{sec:scoring}
\begin{enumerate}
      \item Robots score points for Apples in their scoring zone at the end of the match.
      \item An Apple is considered 'In' a zone if any part of it is within the zone, when
            viewed from above. If it is not clear whether an Apple is in a zone or not, this
            will be determined by the judge or \staff and is entirely at their discretion.
      \item It is possible for Apples to be stacked on other Apples at the end of the match,
            in which case, the above ruling is made separately for each Apple.
            I.e. it is possible that:
            \begin{enumerate}
                  \item An Apple is stacked on a scoring Apple but does itself not score, or
                  \item An Apple is stacked on an Apple that doesn't score but itself does, or
                  \item An Apple is stacked on a scoring Apple that scores differently to itself.
            \end{enumerate}
      \item The scoring zone contains a 'Market Stall' as specified in \ref{spec:scoringZone}
      \item This has two bonus scoring tiers on it, namely the \emph{lower tier} and \emph{upper tier}
      \item Apples that are in these zones at the end of the game, as determined by the above rulings,
            score additional points compared to Apples on the floor in the scoring zone as follows:
      \begin{center}
            \begin{tabular}{lccc}
                  \toprule
                  a   &    Floor   &   Lower tier   &  Upper tier  \\
                  \midrule
                  Red Apple    &    1       &       2        &      3       \\
                  Golden Apple &    2       &       4        &      6       \\
                  Rotten Apple &   -1       &      -2        &     -3       \\
                  \bottomrule
            \end{tabular}
      \end{center}
\end{enumerate}

