\section{Regulations}
\label{sec:regs}

\begin{enumerate}
\item The Judge's decision is final.
\item All robots must be safe.
  \begin{enumerate}
    \item This is defined considering safety concerns including, but not limited
          to:
      \begin{enumerate}
        \item sharp edges;
        \item the effects of impact at speed;
        \item fire risks from the battery (see Regulation~\ref{reg:lipo}).
      \end{enumerate}
    \item No robots will be permitted to compete without passing a safety and
          compliance inspection.
    \item \staff may reinspect your robot and invalidate previous inspections at
          any time.
  \end{enumerate}
\item Any assistance from \org staff and volunteers is provided without
      guarantees.
\item Competitors are expected to behave within the spirit of good
      sportsmanship.
\item Competitors must take reasonable measures to avoid their robot damaging
      the arena, or anything within it, including other robots. This is a
      non-contact sport.
\item Competitors are not permitted in the arena during the competition,
      except to lean in to start robots or where directed by match officials.
\item All robots must be fully autonomous once started. No remote control
      systems are permitted.
\item At the start of each match, all competing robots must fit within a cube
      with edges of length \SI{500}{mm}. Expansion beyond this limit during the
      course of a match is permitted.
\item \label{reg:lipo}
      The Lithium-Polymer battery is the most dangerous part of the electronics
      kit and must be treated accordingly. Whenever a robot is in operation
      its battery must be:
  \begin{enumerate}
    \item securely held in place;
    \item adequately protected from damage even in the presence of damage to the
          rest of the robot;
    \item connected only to the main input of the power board.
  \end{enumerate}
%\item Additional batteries or other energy storage must be explicitly and
%      individually approved by \org before use.
\item A robot's main power switch must be easily accessible and on the top of
      the robot whenever the robot is powered.
%\item All robots must have badge mountings as described in
%      Specification~\ref{spec:badges}.
\item All electronics on a robot must be:
  \begin{enumerate}
    \item securely held in place;
    \item easily removable.
  \end{enumerate}

\item A robot must not have any devices designed to make sound, other
      than where provided directly by \org{}.
\end{enumerate}

