\section{Tournament Format}

The competition takes place in two phases: the league, and the knockouts.

\subsection{League}

\begin{enumerate}
  \item In the league stage, teams will face all other teams at least once.
  \item At the end of each match, \emph{league points} will be awarded as
        follows:
    \begin{enumerate}
      \item The team with the highest game points is awarded 8 league points;
      \item The team with the second-highest game points is awarded 6 league
            points;
      \item The team with the third-highest game points is awarded 4 league
            points;
      \item The team with the fourth-highest game points is awarded 2 league
            points;
      \item In case of any ties, the total number of league points spanned is
            divided by the number of entrants. For instance, if two teams tie
            for second place in a match, that gives a total of 10 league points
            between them (6 for second place and 4 for third), which divided
            equally gives both teams 5 league points.
      \item After points distribution, any disqualified or non-present teams
            have their awarded league points nullified for that match.
    \end{enumerate}
  \item At the end of the league, the total numbers of league points are used as
        seedings for a knockout structure. Teams that placed higher in the
        league will have to compete in fewer matches in the knockout --
        although, all teams will take part in the knockout and thus have a
        chance of winning.
\end{enumerate}

\subsection{Knockouts}

The knockouts span five matches, with the format as follows:

\begin{center}
  \begin{tabular}{r|cccc}
  \toprule
  \textbf{Match} & \textbf{Zone 0} & \textbf{Zone 1} & \textbf{Zone 2} &
                   \textbf{Zone 3} \\
  \midrule
  QF 1 & Seed 3 & Seed 5 & Seed 8 & Seed 10 \\
  QF 2 & Seed 4 & Seed 6 & Seed 7 & Seed 9 \\
  SF 1 & Seed 2
       & 1\textsuperscript{st}, QF 1
       & 3\textsuperscript{rd}, QF 1
       & 2\textsuperscript{nd}, QF 2 \\
  SF 2 & Seed 1
       & 2\textsuperscript{nd}, QF 1
       & 1\textsuperscript{st}, QF 2
       & 3\textsuperscript{rd}, QF 2 \\
  GF & 1\textsuperscript{st}, SF 1
     & 2\textsuperscript{nd}, SF 1
     & 1\textsuperscript{st}, SF 2
     & 2\textsuperscript{nd}, SF 2 \\
  \bottomrule
  \end{tabular}
\end{center}

All ties in the knockout stage are resolved by a decision from the Judge, taking
league position into consideration.

